DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/main.tex
add authors
appendix
..

\title{DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car}
\author{Author One, Author Two\\
\{author1,author2\}@ku.edu\\
University of Kansas, USA\\ 
}

\maketitle
\thispagestyle{empty}
\begin{abstract}
In order to effectively research autonomous vehicles, a real-time capable platform is required. Such 
platforms can be hard to obtain, or build, as the necessary components can be expensive. In this paper, 
we present a low-cost alternative platform that utilizes a Raspberry Pi 3 Model B, along with a single 
external camera sensor, to perform all necessary self-driving operations. A convolutional neural network 
(CNN) is employed and trained with input from a human driver to navigate a custom made track. We display 
the real-time efficacy of our platform in experiments with varying amount of computational resources 
and/or intensive AI workloads. To gain a better understanding of our platform's potential, we compare it 
to other embedded computing platforms to determine which are suitable for autonomous driving research.
\end{abstract}

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{related}
\input{conclusion}
%-------------------------------------------------------------------------
\bibliographystyle{abbrv}
\bibliography{reference}

\appendix
\end{document}

>>>>

\title{DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car}
\author{Michael Garrett Bechtel, Elise McEllhiney, Heechul Yun\\
\{m783b224, e908m429, heechul.yun\}@ku.edu\\
University of Kansas, USA\\ 
}

\maketitle
\thispagestyle{empty}
\begin{abstract}
In order to effectively research autonomous vehicles, a real-time
capable platform is required. Such platforms can be hard to obtain, or
build, as the necessary components can be expensive. In this paper,
we present a low-cost alternative platform that utilizes a Raspberry
Pi 3 Model B, along with a single external camera sensor, to perform
all necessary self-driving operations. A convolutional neural network
(CNN) is employed and trained with input from a human driver to
navigate a custom made track. We display the real-time efficacy of our
platform in experiments with varying amounts of computational resources
and/or intensive AI workloads. To gain a better understanding of our
platform's potential, we compare it to other embedded computing
platforms to determine which are suitable for autonomous driving
research.
\end{abstract}

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{comparison}
\input{related}
\input{conclusion}
%-------------------------------------------------------------------------
\bibliographystyle{abbrv}
\bibliography{reference}

\appendix
\input{appendix}
\end{document}
